Statistical Methods for Replicability Assessment

### 2020-03-06 response.tex

\documentclass[]{article}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{courier}
\usepackage[round]{natbib}
\usepackage{subcaption}
\usepackage{xcolor}

\DeclareMathOperator{\var}{var}
\DeclareMathOperator*{\argmax}{arg\,max}

\setlength{\parindent}{15pt}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}

\newcommand{\EE}{\mathbb{E}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}
\newcommand*{\vertbar}{\rule[-1ex]{0.5pt}{2.5ex}}
\newcommand*{\horzbar}{\rule[.5ex]{2.5ex}{0.5pt}}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\diag}{diag}

\newcommand{\KHComment}[1]{{\color{green!50!gray} (KH: #1)}}
\newcommand{\WFComment}[1]{{\color{red!50!gray} (WF: #1)}}

\begin{document}

\begin{itemize}

\item Kenneth Hung
\item Response to reviews
\item Reference: Statistical Methods for Replicability Assessment

\end{itemize}

We thank both referees for their thoughtful questions and helpful suggestions. Please find a point-by-point response below.

\section{Response to Reviewer 1}

\begin{itemize}

\item {\em The current paper provides some previously lacking statistical rigor in the analysis of an impactful replication study, and establishes that publication bias due to selection of significant effects is consistent with the observed findings. This is important because it provides one possible explanation or mechanism for this widely discussed outcome. I believe this aspect of the paper is important enough that it would make sense to include it as a focal point in the abstract of the paper.}

We agree and have added this to the abstract.

\item {\em I found the statement of Assumption 1 a bit confusing to parse. It’s a run-on sentence. The word ``literally'' can be omitted in the preceding paragraph as well.}

Noted and rewritten.

\item {\em The plots on the right sides of Figures 2--4 are excellent for providing intuition. Is there a way to make this intuition clear as well for the estimators of FDP? I suspect it should be obvious that the estimates of FDP will be lower than $64\%$ when applied to the RP:P data, perhaps there is a figure that would show this.}

We believe that Figure 6 is the best at delivering the intuition for where this conclusion came from, and we have added more detailed descriptions there now.

\end{itemize}

\section{Response to Reviewer 2}

\begin{itemize}

\item {\em Should these both be $35\%$? Do you mean that all of the $35\%$ that declined did so by at least $20\%$, or that $35\%$ of the $35\%$ that declined did so by at least $20\%$?}

For this data set the estimates for how many declined, and how many declined by $20\%$, happen to coincide, but we understand why this created confusion.

We mean that all of the $35\%$ that declined did so by at least $20\%$ (or at least, that our estimates for how many effects declined, and how many effects declined by $20\%$, happen to coincide). We understand why this created confusion, however, and we have replaced $20\%$ with $25\%$.

\item {\em You mention ``in contrast to the earlier internal comparison method'' (pg 12) but it’s not very clear what it refers to and the phrase doesn’t appear again in the paper. I think you mean the the estimator at the top of the page?}

Yes, that is what we meant. We have rewritten to clarify what we are referring to.

\item {\em In general, I found it quite easy to get lost in the notation. You might find a notation table useful for clarity.}

Thank you for this suggestion, we have added a table.

\item {\em You comment on the sizing of replication studies to achieve fixed power under the original effect size, and how this negatively impacts replication chances due to inflated original effect sizes. It seems like there could be a role for post-selection inference here to more appropriately size those replication studies. If so, it might be an interesting point for the discussion.}

Yes, we agree this is interesting and we have added to ``Future work'' section.

\item {\em As an aside, I would actually question Assumption 1. I think strongly significant results are often significantly easier to publish than studies with $p$-values near $0.05$. This would be in the opposite direction of the pile-up phenomenon that you mention, though certainly both could happen together in different regions of $p$-value. I suppose that if recent suggestions for a much lower significance threshold were accepted, Assumption 1 would likely hold more strongly.}

We agree that it would be better to have more detailed information about this, especially for meta-analyses of studies in the recent past or future. With all the attention paid to replicability recently, it is likely that scientists' application of the $5\%$ significance threshold has become less automatic since 2008, when the RP:P studies were published. A more sophisticated assumption can replace Assumption 1 if we have a model for the propensity for publication, e.g.\ \citet{Andrews:2018vh}. We hope future work can refine this. With the additional data from preprints and registered reports, it might be possible to try assessing how behavior is changing.

\bibliographystyle{plainnat}
\bibliography{papers,additional}

\end{itemize}

\end{document}

### 2020-03-06 paper.tex
accepted version

\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{caption}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\newlist{inlinelist}{enumerate*}{1}
\setlist*[inlinelist]{label=(\arabic*)}
\usepackage[totalwidth=450pt, totalheight=630pt]{geometry}
\usepackage{graphicx}
\PassOptionsToPackage{hyphens}{url} % pass options to url autoloaded by hyperref
\usepackage[pdfencoding=auto, psdextra]{hyperref} % hyperref must be loaded before cleveref
\usepackage{mathrsfs}
\usepackage{multirow}
\usepackage[round]{natbib} % natbib must be loaded before algorithm2e
\usepackage[linesnumbered, ruled]{algorithm2e} % algorithm2e must be loaded before cleveref
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{verbatim}
\usepackage{xcolor}

@@

\newcommand{\WFcomment}[1]{{\color{red!40!gray} (WF: #1)}}
\newcommand{\KHcomment}[1]{{\color{green!40!gray} (KH: #1)}}

% Uncomment this line to get rid of my comments
% \renewcommand{\WFcomment}[1]{}
% \renewcommand{\KHcomment}[1]{}

@@

\title{Statistical Methods for Replicability Assessment}
\date{\today}
\author{
  Kenneth Hung\thanks{Department of Mathematics, University of California, Berkeley} \and
  William Fithian\thanks{Department of Statistics, University of California, Berkeley}
}
\maketitle

\begin{abstract}
  Large-scale replication studies like the Reproducibility Project: Psychology (RP:P) provide invaluable systematic data on scientific replicability, but most analyses and interpretations of the data fail to agree on the definition of ``replicability'' and disentangle the inexorable consequences of known selection bias from competing explanations. We discuss three concrete definitions of replicability based on
  \begin{inlinelist}
    \item whether published findings about the signs of effects are mostly correct,
    \item how effective replication studies are in reproducing whatever true effect size was present in the original experiment, and
    \item whether true effect sizes tend to diminish in replication.
  \end{inlinelist}
  We apply techniques from multiple testing and post-selection inference to develop new methods that answer these questions while explicitly accounting for selection bias. Re-analyzing the RP:P data, we estimate that $22$ out of $68$ ($32\%$) original directional claims were false (upper confidence bound $47\%$); by comparison, we estimate that among claims significant at the stricter significance threshold $0.005$, only $2.2$ out of $33$ ($7\%$) were directionally false (upper confidence bound $18\%$). In addition, we compute selection-adjusted confidence intervals for the difference in effect size between original and replication studies and, after adjusting for multiplicity, identify five ($11\%$) which exclude zero (exact replication). We estimate that the effect size declined by at least $20\%$ in the replication study relative to the original study in $16$ of the $46$ ($35\%$) study pairs (lower confidence bound $11\%$). Our methods make no distributional assumptions about the true effect sizes.
\end{abstract}

@@

  While the RP:P dataset is an invaluable resource, scientists disagree on how to quantify or measure replicability \citep{Goodman:2016bo,Amrhein:2017en}. \citet[OSC;][]{OpenScienceCollaboration:2015cn} reported three main metrics: it found that $64\%$ ($= 1 - 36\%$) of the replication studies did not find statistically significant results in the same direction as the original studies, that $53\%$ ($= 1 - 47\%$) of $95\%$ confidence intervals for the replication studies do not contain the point estimates for their corresponding original studies, and that $83\%$ of the effect size estimates declined from original studies to replications. All three summary statistics were widely reported as indicating a dire crisis for the credibility of experimental psychology research. For example, the {\em Washington Post} reported that RP:P ``affirms that the skepticism [of published results] was warranted'' \citep{Achenbach:2015vi}; the {\em Economist} noted that OSC ``managed to replicate satisfactorily the results of only $39\%$ of the studies investigated'' \citep{Anonymous:uoQKTVTm}; and the {\em New York Times} reported that ``more than half of the findings did not hold up when retested'' \citep{Carey:2015wp}.

@@

@@

  As we will see, however, none of the three reported metrics can be taken at face value as {\em estimates} of the answers to the corresponding questions, due to the confounding factor of pervasive selection bias. By using techniques from multiple testing and post-selection inference, we will develop methods to rigorously address these questions without assuming a model for the prior distribution of effect sizes. For the RP:P data we estimate the rate of false directional claims at roughly $32\%$ among studies with $p < 0.05$, which would be considered unacceptably high in most multiple testing applications. By contrast, among studies with $p < 0.005$, a lower threshold proposed by \citet{Benjamin:2018gh}, our estimate drops to $7\%$, with an upper confidence bound of $18\%$. We also compute confidence intervals for the effect shift in each individual study pair and find that, after adjusting for multiplicity, about $11\%$ of the intervals exclude zero, an idealized null hypothesis of perfect replication. For effect decline, we find in aggregate that $35\%$ of the true effects declined, and $35\%$ declined by at least $20\%$.

@@

  \paragraph{Effect size decline} The null hypothesis for effect size decline is closely related to effect shift, and can be formalized as the null hypothesis where the true effect size has declined by no more than a fraction $\rho \in [0, 1]$:
  \[
    H_i^{D,\rho}:\; S_i \,\cdot\, \theta_{i,R} \ge S_i \,\cdot\, (1 - \rho) \theta_{i,O}.
  \]
  If $S_i = +1$ and $\rho=0.2$, for example, rejecting $H_i^{D,\rho}$ amounts to an assertion that $\theta_{i,R} < 0.8 \,\theta_{i,O}$, i.e. the true effect declined by more than $20\%$, or is negative.

@@

@@

\subsection{Selection bias model}
  Model~\eqref{eq:trunc-model} assumes that results are only published if they achieved statistical significance at some conventional threshold level $\ao$, which is $0.05$ in our data. While this assumption is not literally true in the case of RP:P since some original $p$-values are above $0.05$, we note that the model can be relaxed to the following milder assumption:
  \begin{assumption}
    \label{ass:sig-enough}
    $p_O < \ao$ is ``significant enough'': that is, not all results with significant $p$-values are necessarily published, but a result with $p_O < \ao$ would have been equally likely to be published (or selected for replication), had the $p$-value taken on some other statistically significant value.
  \end{assumption}

  If \Cref{ass:sig-enough} holds, then we can model the original test statistics as following their theoretical distribution, truncated to the event where the corresponding $p$-values are below $\ao$, as in Model~\ref{eq:trunc-model}.

  Note that \Cref{ass:sig-enough} contemplates a fairly straightforward mechanism for selection on statistical significance, which may not be adequate to describe the effects of more complex and difficult-to-model QRPs. In particular, $p$-hacking --- the iterative tweaking of an analysis until the $p$-value drops below the researcher's desired significance level $\ao$ --- is commonly suspected to produce a pileup of $p$-values just below the significance threshold \citep[see e.g.][]{Simonsohn:2014fa}. Because $p$-hacking is such a vaguely defined practice, it is unclear how we might incorporate it into our model, but in any case there is no evidence of a pileup just below $0.05$ in the original RP:P studies (see \Cref{fig:fdp-original}).

@@

  \paragraph{Directional FDP at smaller thresholds} One proposal to address the replicability crisis is to lower the conventional significance threshold from $\ao=0.05$ to some smaller value $\alpha$, such as $0.005$ \citep{Benjamin:2018gh}. As suggested by \citet{Goodman:2013kj}, an empirical method to evaluate the hypothetical scenario with a smaller threshold can be helpful. We now discuss methods for inference on the directional FDP for those studies with $p_O < \alpha < \ao$, based on comparing the number of adjusted $p$-values below $\alpha$ with the number above $\lambda\ao$, for some $\lambda > \alpha/\ao$. We call this method the {\em external comparison method} in contrast to the earlier {\em internal comparison method}. This method will be less conservative as we are not constrained to only using the $p$-values in $[0, \alpha)$.

@@

  \begin{proof}
    Leveraging the fact that $\eta' \eta_\perp = 0$, we reparametrize the joint distribution of $(Z_1, Z_2)$ under the null such that $\delta$ is a parameter, i.e.
    \[
      \begin{bmatrix} D \\ M \end{bmatrix} =
      \begin{bmatrix} \eta' \mu \\ \eta_\perp' \mu \end{bmatrix}
      \sim N\left(
      \begin{bmatrix} \delta \\ \eta_\perp' \mu \end{bmatrix},
      \begin{bmatrix}
        \|\eta\|^2 & 0 \\
        0 & \|\eta\|^2
      \end{bmatrix}\right) 1_{\{Z_1 \in A\}}.
    \]
    In particular, the event $Z_1 \in A$ can be rewritten as
    \[
      D \in \frac{\|\eta\|^2 A - \eta_2 M}{\eta_1}.
    \]
    And so the distribution of $D$ conditional on $M$ under $H_0^\delta$ is a truncated Gaussian distribution,
    \[
      [D \mid M] \sim N\left(\delta, \|\eta\|^2\right) 1_{\left\{D \in \frac{\|\eta\|^2 A - \eta_2 M}{\eta_1}\right\}}
    \]
    and we obtain a valid test by rejecting when $D$ is smaller than the $\frac{0.05}{2}$-quantile or larger than the $\left(1 - \frac{0.05}{2}\right)$-quantile.
  \end{proof}

@@

  We implemented our method with $\lambda = 0.5$ to estimate the number of one-sided nulls and the directional FDP.\footnote{Choosing $\lambda = 0.5$ follows the convention in the multiple testing literature for a bias-variance trade off: if $\lambda$ is too small, many true discoveries are counted as false; if $\lambda$ is too big, the estimator can have large variance.} The adjusted original $p$-values and replication $p$-values are given in \Cref{fig:fdp-original,fig:fdp-replication} respectively. Using the original $p$-values, we estimate that $22$ of the $68$ ($32\%$) original directional claims are false, with a $95\%$ upper confidence bound of $47\%$. Using the replication $p$-values, we estimate that $32$ of the $68$ ($47\%$) original directional claims incorrectly predict the direction of the replication effect, with a $95\%$ upper confidence bound of $63\%$. In particular both of our FDP estimates are much lower than the $64\%$ which could be suggested by a naive reading of RP:P \citep[e.g.][]{Baker:2015kd}. These numbers are summarized again in \Cref{tbl:fdp-sim} later. Furthermore, while we can compute a lower confidence bound, it will always be $0\%$ as the data is obviously consistent with many null hypotheses being slightly false.
  \begin{figure}[htbp]
    \centering
    \begin{subfigure}[t]{0.49\hsize}
      \centering
      \includegraphics[width=\hsize]{fdp-original}
      \caption{Histogram of the adjusted original $p$-values.}
    \label{fig:fdp-original}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.49\hsize}
      \centering
      \includegraphics[width=\hsize]{fdp-replication}
      \caption{Histogram of the replication $p$-values.}
    \label{fig:fdp-replication}
    \end{subfigure}
    \caption{Histograms of $p$-values. We estimate the expected number of true nulls in each bin by the method from \citet{Storey:2002vj}, shown by the horizontal red line. A net excess of $p$-values above this line means false directional claims.}
  \end{figure}

@@

  More generally, we used the hypothesis $H^{D,\rho}$ to estimate the proportion of effect sizes that declined by at least a fraction of $\rho$. The underestimate, overestimate and the $90\%$ confidence interval are given in \Cref{fig:effect-decline-range}. For example, we estimate that $16$ of the $46$ effect sizes ($35\%$ (with a $95\%$ lower confidence bound $11\%$) decreased by at least $20\%$, even after adjusting for selection on measurement noise. Note that this does not exclude explanations by other forms of selection, e.g.\ selecting a large effect when there is a random effect.
  \begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{effect-decline-range}
    \caption{The underestimate, overestimate and the $90\%$ confidence interval. The lower black line is the underestimate, the high black line is the overestimate and the gray band is the $90\%$ confidence interval.}
  \label{fig:effect-decline-range}
  \end{figure}

@@

  First, selection for significance is an inevitable consequence of the current scientific process. Our adjustments for selection is admittedly crude, but necessitated by the limitations in the given data. With more available information, a better model for selection can be used. For example, with the advancement of preregistration, we can use the external comparison method to produce less conservative estimates of the directional FDP at level $\alpha = 0.05$ if we have more information about statistically nonsignificant studies. With more replications carried out, we can estimate the publication bias model in \citet{Andrews:2018vh} more precisely; together with higher powered design in replications \citep[e.g.][]{Camerer:2018de}, we can enhance the precision of our estimators and power of our tests.

@@

\section*{Supplement}

  The supplement is available in the git repository, or directly on \url{https://github.com/kenhungkk/assessing-replicability/raw/public/supplement.pdf}.

@@

  We thank Marcel A L M van Assen, Yoav Benjamini, Dean Eckles, Philip B Stark, Jacob Steinhardt, Jonathan Taylor, Alexa Tulett, Stefan Wager, Daniel Yekutieli, and Bin Yu for helpful comments and discussions.

\Urlmuskip=0mu plus 1mu\relax
\bibliographystyle{plainnat}
\bibliography{papers,additional}

>>>>

\documentclass[aoas, preprint]{imsart}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{caption}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\newlist{inlinelist}{enumerate*}{1}
\setlist*[inlinelist]{label=(\arabic*)}
\usepackage[totalwidth=450pt, totalheight=630pt]{geometry}
\usepackage{graphicx}
\PassOptionsToPackage{hyphens}{url} % pass options to url autoloaded by hyperref
\usepackage[pdfencoding=auto, psdextra]{hyperref} % hyperref must be loaded before cleveref
\usepackage{mathrsfs}
\usepackage{multirow}
\usepackage[round]{natbib} % natbib must be loaded before algorithm2e
\usepackage[linesnumbered, ruled]{algorithm2e} % algorithm2e must be loaded before cleveref
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{verbatim}
\usepackage{xcolor}

% arXiv number
\arxiv{arXiv:1903.08747}

% custom definitions
\startlocaldefs

@@

\endlocaldefs

@@

\begin{frontmatter}

\title{Statistical Methods for Replicability Assessment}
\runtitle{Statistical Methods for Replicability Assessment}

\begin{aug}
  \author{\fnms{Kenneth} \snm{Hung}\corref{}\ead[label=e1]{kenhung@berkeley.edu}}
  \and
  \author{\fnms{William} \snm{Fithian}\ead[label=e2]{wfithian@berkeley.edu}}

  \runauthor{K. Hung and W. Fithian}

  \affiliation{University of California, Berkeley}

  \address{Department of Mathematics\\ 951 Evans Hall, Suite 3840\\ Berkeley, CA 94720-3840\\
  \printead{e1}}

  \address{Department of Statistics\\ 301 Evans Hall\\ Berkeley, CA 94720\\
          \printead{e2}}

\end{aug}

\begin{abstract}
  Large-scale replication studies like the Reproducibility Project: Psychology (RP:P) provide invaluable systematic data on scientific replicability, but most analyses and interpretations of the data fail to agree on the definition of ``replicability'' and disentangle the inexorable consequences of known selection bias from competing explanations. We discuss three concrete definitions of replicability based on
  \begin{inlinelist}
    \item whether published findings about the signs of effects are mostly correct,
    \item how effective replication studies are in reproducing whatever true effect size was present in the original experiment, and
    \item whether true effect sizes tend to diminish in replication.
  \end{inlinelist}
  We apply techniques from multiple testing and post-selection inference to develop new methods that answer these questions while explicitly accounting for selection bias. Our analyses suggest that the RP:P dataset is largely consistent with publication bias due to selection of significant effects. The methods in this paper make no distributional assumptions about the true effect sizes.
\end{abstract}

\begin{keyword}[class=MSC]
\kwd[Primary ]{62F03}
\kwd[; secondary ]{62P25}
\end{keyword}

\begin{keyword}
\kwd{replicability}
\kwd{multiple testing}
\kwd{post-selection inference}
\kwd{publication bias}
\kwd{meta-analysis}
\end{keyword}

\end{frontmatter}

@@

  While the RP:P dataset is an invaluable resource, scientists disagree on how to quantify or measure replicability \citep{Goodman:2016bo,Amrhein:2017en}. \citet[OSC;][]{OpenScienceCollaboration:2015cn} reported three main metrics: it found that $64\%$ ($= 1 - 36\%$) of the replication studies did not find statistically significant results in the same direction as the original studies, that $53\%$ ($= 1 - 47\%$) of $95\%$ confidence intervals for the replication studies do not contain the point estimates for their corresponding original studies, and that $83\%$ of the effect size estimates declined from original studies to replications. All three summary statistics were widely reported as indicating a dire crisis for the credibility of experimental psychology research. For example, the {\em Washington Post} reported that RP:P ``affirms that the skepticism [of published results] was warranted'' \citep{Achenbach:2015vi}; the {\em Economist} noted that OSC ``managed to replicate satisfactorily the results of only $39\%$ of the studies investigated'' \citeyearpar{Anonymous:uoQKTVTm}; and the {\em New York Times} reported that ``more than half of the findings did not hold up when retested'' \citep{Carey:2015wp}.

@@

\subsection{Three definitions of replicability}

@@

  As we will see, however, none of the three reported metrics can be taken at face value as {\em estimates} of the answers to the corresponding questions, due to the confounding factor of pervasive selection bias. By using techniques from multiple testing and post-selection inference, we will develop methods to rigorously address these questions without assuming a model for the prior distribution of effect sizes. For the RP:P data we estimate the rate of false directional claims at roughly $32\%$ among studies with $p < 0.05$, which would be considered unacceptably high in most multiple testing applications. By contrast, among studies with $p < 0.005$, a lower threshold proposed by \citet{Benjamin:2018gh}, our estimate drops to $7\%$, with an upper confidence bound of $18\%$. We also compute confidence intervals for the effect shift in each individual study pair and find that, after adjusting for multiplicity, about $11\%$ of the intervals exclude zero, an idealized null hypothesis of perfect replication. For effect decline, we find in aggregate that $35\%$ of the true effects declined, and $22\%$ declined by at least $25\%$.

@@

  \paragraph{Effect size decline} The null hypothesis for effect size decline is closely related to effect shift, and can be formalized as the null hypothesis where the true effect size has declined by no more than a fraction $\rho \in [0, 1]$:
  \[
    H_i^{D,\rho}:\; S_i \,\cdot\, \theta_{i,R} \ge S_i \,\cdot\, (1 - \rho) \theta_{i,O}.
  \]
  If $S_i = +1$ and $\rho=0.25$, for example, rejecting $H_i^{D,\rho}$ amounts to an assertion that $\theta_{i,R} < 0.75 \,\theta_{i,O}$, i.e. the true effect declined by more than $25\%$, or is negative.

@@

  To facilitate the rest of the paper, we recapitulate the notations above in \Cref{tbl:notation}.
  \begin{table}[htbp]
    \centering
    \begin{tabularx}{\textwidth}{lX}
      \toprule
      Symbol & Meaning \\
      \midrule
      $\theta_{i,O}$, $\theta_{i,R}$ & True effect sizes in the original and replication $i$-th studies \\
      $\htheta_{i,O}$, $\htheta_{i,R}$ & Effect size estimates in the original and replication $i$-th studies \\
      $\sigma_{i,O}$, $\sigma_{i,R}$ & Standard errors in the original and replication $i$-th studies \\
      $S_i$ & Sign of the original $i$-th study \\
      $H_i^{S,O}$, $H_i^{S,R}$ & Hypothesis that a type S error has occurred in the original and replication $i$-th studies  \\
      $H_i^E = H_i^{E,0}$, $H_i^{E,\delta}$ & Hypothesis that the true effect has shifted by $\delta$ from the original to the replication $i$-th study \\
      $H_i^{D,\rho}$ & Hypothesis that the true effect size has declined by no more than the fraction $\rho$ \\
      \bottomrule
    \end{tabularx}
    \caption{Summary of notations introduced.}
  \label{tbl:notation}
  \end{table}

@@

\subsection{Selection bias model}
  Model~\eqref{eq:trunc-model} assumes that results are only published if they achieved statistical significance at some conventional threshold level $\ao$, which is $0.05$ in our data. While this assumption is not true in the case of RP:P since some original $p$-values are above $0.05$, we note that the model can be relaxed to the following milder assumption:
  \begin{assumption}
    \label{ass:sig-enough}
    $p_O < \ao$ is ``significant enough'': a result with $p_O < \ao$ would be equally likely to be published (or selected for replication), if the $p$-value were some other statistically significant value.
  \end{assumption}

  \Cref{ass:sig-enough} allows some significant $p$-values to go unpublished. If it holds, then we can model the original test statistics as following their theoretical distribution, truncated to the event where the corresponding $p$-values are below $\ao$, as in Model~\ref{eq:trunc-model}.

  Note that \Cref{ass:sig-enough} contemplates a fairly straightforward mechanism for selection on statistical significance, which may not be adequate to describe the effects of more complex and difficult-to-model QRPs. In particular, $p$-hacking --- the iterative tweaking of an analysis until the $p$-value drops below the researcher's desired significance level $\ao$ --- is commonly suspected to produce a pileup of $p$-values just below the significance threshold \citep[see e.g.][]{Simonsohn:2014fa}. Because $p$-hacking is such a vaguely defined practice, it is unclear how we might incorporate it into our model, but in any case there is no evidence of a pileup just below $0.05$ in the original RP:P studies (see \Cref{fig:fdp-original}). We will reconsider the validity of \Cref{ass:sig-enough} in \Cref{sec:discussion}.

@@

  \paragraph{Directional FDP at smaller thresholds} One proposal to address the replicability crisis is to lower the conventional significance threshold from $\ao=0.05$ to some smaller value $\alpha$, such as $0.005$ \citep{Benjamin:2018gh}. As suggested by \citet{Goodman:2013kj}, an empirical method to evaluate the hypothetical scenario with a smaller threshold can be helpful. We now discuss methods for inference on the directional FDP for those studies with $p_O < \alpha < \ao$, based on comparing the number of adjusted $p$-values below $\alpha$ with the number above $\lambda\ao$, for some $\lambda > \alpha/\ao$. We call this method the {\em external comparison method} in contrast to the earlier {\em internal comparison method} that bases on \eqref{eq:Bgest}. This method will be less conservative as we are not constrained to only using the $p$-values in $[0, \alpha)$.

@@

  \begin{proof}
    Leveraging the fact that $\eta' \eta_\perp = 0$, we reparametrize the joint distribution of $(Z_1, Z_2)$ under the null such that $\delta$ is a parameter, i.e.
    \[
      \begin{bmatrix} D \\ M \end{bmatrix} =
      \begin{bmatrix} \eta' Z \\ \eta_\perp' Z \end{bmatrix}
      \sim N\left(
      \begin{bmatrix} \delta \\ \eta_\perp' \mu \end{bmatrix},
      \begin{bmatrix}
        \|\eta\|^2 & 0 \\
        0 & \|\eta\|^2
      \end{bmatrix}\right) 1_{\{Z_1 \in A\}}.
    \]
    In particular, the event $Z_1 \in A$ can be rewritten as
    \[
      D \in \frac{\|\eta\|^2 A - \eta_2 M}{\eta_1}.
    \]
    And so the distribution of $D$ conditional on $M$ under $H_0^\delta$ is a truncated Gaussian distribution,
    \[
      [D \mid M] \sim N\left(\delta, \|\eta\|^2\right) 1_{\left\{D \in \frac{\|\eta\|^2 A - \eta_2 M}{\eta_1}\right\}}
    \]
    and we obtain a valid test by rejecting when $D$ is smaller than the $\frac{0.05}{2}$-quantile or larger than the $\left(1 - \frac{0.05}{2}\right)$-quantile.
  \end{proof}

@@

  We implemented our method with $\lambda = 0.5$ to estimate the number of one-sided nulls and the directional FDP.\footnote{Choosing $\lambda = 0.5$ follows the convention in the multiple testing literature for a bias-variance trade off: if $\lambda$ is too small, many true discoveries are counted as false; if $\lambda$ is too big, the estimator can have large variance.} The adjusted original $p$-values and replication $p$-values are given in \Cref{fig:fdp-original,fig:fdp-replication} respectively. Using the original $p$-values, we estimate that $22$ of the $68$ ($32\%$) original directional claims are false, with a $95\%$ upper confidence bound of $47\%$. Using the replication $p$-values, we estimate that $32$ of the $68$ ($47\%$) original directional claims incorrectly predict the direction of the replication effect, with a $95\%$ upper confidence bound of $63\%$. In particular both of our FDP estimates are much lower than the $64\%$ which could be suggested by a naive reading of RP:P \citep[e.g.][]{Baker:2015kd}. These numbers are summarized again in \Cref{tbl:fdp-sim} later. Furthermore, while we can compute a lower confidence bound, it will always be $0\%$ as the data is obviously consistent with many null hypotheses being slightly false.
  \begin{figure}[htbp]
    \centering
    \begin{subfigure}[t]{0.49\hsize}
      \centering
      \includegraphics[width=\hsize]{fdp-original}
      \caption{Histogram of the adjusted original $p$-values.}
    \label{fig:fdp-original}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.49\hsize}
      \centering
      \includegraphics[width=\hsize]{fdp-replication}
      \caption{Histogram of the replication $p$-values.}
    \label{fig:fdp-replication}
    \end{subfigure}
    \caption{Method from \citet{Storey:2002vj} as demonstrated using histograms of $p$-values. We estimate the number of true nulls by conservatively assuming that every hypothesis right of the vertical red line to be true. Since the $p$-value under the null is superuniform, on average there are fewer null hypotheses left of the line than right of the line. Our overestimate of the number of true nulls in each bin is shown by the horizontal red line. A net excess of $p$-values above this line means false directional claims.}
  \end{figure}

@@

  More generally, we used the hypothesis $H^{D,\rho}$ to estimate the proportion of effect sizes that declined by at least a fraction of $\rho$. The underestimate, overestimate and the $90\%$ confidence interval are given in \Cref{fig:effect-decline-range}. For example, we estimate that $10$ of the $46$ effect sizes ($22\%$) decreased by at least $25\%$, even after adjusting for selection on measurement noise. Note that this does not exclude explanations by other forms of selection, e.g.\ selecting a large effect when there is a random effect.
  \begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{effect-decline-range}
    \caption{The underestimate, overestimate and the $90\%$ confidence interval. The lower black line is the underestimate, the high black line is the overestimate and the gray band is the $90\%$ confidence interval.}
  \label{fig:effect-decline-range}
  \end{figure}

@@

  First, selection for significance is an inevitable consequence of the current scientific process. Our adjustments for selection allows not only better analysis, but also more informed design of future replication studies, e.g.\ better power calculations for and sizing of replications. While these adjustments are admittedly crude, they are necessitated by the limitations in the given data. With more available information, a better model for selection can be used. For example, with the advancement of preregistration, we can use the external comparison method to produce less conservative estimates of the directional FDP at level $\alpha = 0.05$ if we have more information about statistically nonsignificant studies. With more replications carried out, we can estimate the publication bias model in \citet{Andrews:2018vh} more precisely, which allows different propensity for publication for different statistical significant $p$-values as opposed to \Cref{ass:sig-enough}. Together with higher powered design in replications \citep[e.g.][]{Camerer:2018de}, we can enhance the precision of our estimators and power of our tests.

@@

@@

  We thank Marcel A L M van Assen, Yoav Benjamini, Dean Eckles, Philip B Stark, Jacob Steinhardt, Jonathan Taylor, Alexa Tulett, Stefan Wager, Daniel Yekutieli, and Bin Yu for helpful comments and discussions. In addition, we are grateful to our two anonymous reviewers for their helpful suggestions which have improved the paper.

\begin{supplement}
  \sname{Supplement A}\label{suppA}
  \stitle{Supplement to ``Statistical Methods for Replicability Assessment''}
  \slink[url]{https://github.com/kenhungkk/assessing-replicability/raw/public/supplement.pdf}
  \sdescription{We evaluate our approximation of $t$-distributions by normal distributions, as well as detail considerations made for individual studies.}
\end{supplement}

\Urlmuskip=0mu plus 1mu\relax
\bibliographystyle{imsart-nameyear}
\bibliography{papers,additional}
